### 2023-04-20 source/paper/appendix_figures.tex
Just in case again...

  \begin{figure}[h]
    \caption{Effect of Anti-Drug Abuse Act on Drug-related Arrest Rate of Adult Black Men, Comparing States with High and Low Black Adult Drug-Related Arrest Rates}
    \centering
    \includegraphics[width=1\textwidth]{eventstudy/high_drug_use/high_drug_eventstudy_1986_extended_years.png}
    \label{fig:b1}
  \end{figure}
  \begin{footnotesize}
    \noindent Note: footnote TO BE UPDATED
  \end{footnotesize}

>>>>

  \begin{figure}[h]
    \caption{Effect of Anti-Drug Abuse Act on Drug-related Arrest Rate of Adult Black Men, Comparing States with High and Low Black Adult Drug-Related Arrest Rates}
    \centering
    \includegraphics[width=1\textwidth]{eventstudy/high_drug_use/high_drug_eventstudy_1986_extended_years.png}
    \label{fig:b1}
  \end{figure}
  \begin{footnotesize}
    \noindent Note: This figure reports coefficients from the estimation of equation \ref{eq:state_level_es} evaluating the impact of the Anti-Drug Abuse Act of 1986 on arrest rates per 100,000 related to drug violations using CPS and UCR data from 1982-1992. Event time $0 \coloneqq 1986$. The coefficients represent the change in outcomes for high-drug arrest states relative to non-high-drug arrest states, where high black adult drug arrest states are defined to be those above the 75th percentile in 1984. The sample is defined as black males aged 18-24 in 1986 who were not incarcerated at the time of the survey. Control variables include population and unemployment rates at the state-year level. Right tail arrest rate outliers were winsorized at the 95\% level.
  \end{footnotesize}

### 2023-04-20 source/paper/figures.tex
Just in case again...

   % Arrest rate pretrends

@@

  % High vs low arrest states pretrends

@@

  \begin{figure}[h]
    \centering
    \caption{Additional Pretrend Testing for Coefficients from Figure 7}%
    \subfloat[\centering Linear pretrend]{{\includegraphics[width=7cm]{pretrends/power/firststage_linear_ab1986.png} }}%
    \qquad
    \subfloat[\centering Quadratic pretrend]{{\includegraphics[width=7cm]{pretrends/power/firststage_quad_ab1986.png} }}%
    \label{fig:pretrends_roth}%
  \end{figure}

  \begin{footnotesize}
    \noindent Note: These two figures were constructed using an R package written by \cite{roth2022}. The figures and pretrend statistics were calculated using the estimated coefficients from Figure 7 and their corresponding covariance matrixes. The slope in Figure A was constructed such that the power would be about 0.5, while the quadratic trend in Figure B was chosen visually.

@@

\begin{figure}[h]
  \centering
  \caption{Effect of Fair Sentencing Act on the College Enrollment Rate of Adult Black Men, Comparing High and Low-Intensity States}%
  \subfloat[\centering Using adults arrests]{{\includegraphics[width=7cm]{eventstudy/high_drug_use/reducedform_ab1986.png} }}%
  \qquad
  \subfloat[\centering Using juvenile arrests]{{\includegraphics[width=7cm]{eventstudy/high_drug_use/reducedform_jb1986.png} }}%
  \label{fig:rs_es_1986}%
\end{figure}

@@

\begin{figure}[h]
  \centering
  \caption{Effect of Fair Sentencing Act on the College Enrollment Rate of Adult Black Men, Comparing High and Low-Intensity States}%
  \subfloat[\centering Using adults arrests]{{\includegraphics[width=7cm]{eventstudy/high_drug_use/reducedform_ab1986.png} }}%
  \qquad
  \subfloat[\centering Using juvenile arrests]{{\includegraphics[width=7cm]{eventstudy/high_drug_use/reducedform_jb2010.png} }}%
  \label{fig:rf_jb_es_2010}%
\end{figure}

>>>>

   % Arrest rate pre-trends

@@

  % High vs low arrest states pre-trends

@@

  \begin{figure}[h]
    \centering
    \caption{Additional Pre-trend Testing for Coefficients from Figure 7}%
    \subfloat[\centering Linear pre-trend]{{\includegraphics[width=7cm]{pretrends/power/firststage_linear_ab1986.png} }}%
    \qquad
    \subfloat[\centering Quadratic pre-trend]{{\includegraphics[width=7cm]{pretrends/power/firststage_quad_ab1986.png} }}%
    \label{fig:pre-trends_roth}%
  \end{figure}

  \begin{footnotesize}
    \noindent Note: These two figures were constructed using an R package written by Roth (2022). The figures and pre-trend statistics were calculated using the estimated coefficients from Figure 7 and their corresponding covariance matrixes. The slope in Figure A was constructed such that the power would be about 0.5, while the quadratic trend in Figure B was chosen visually. The blue expectation after pretesting coefficients represents the expected value of the coefficients conditional on passing the pre-test under the hypothesized trend.

@@

\begin{figure}[h]
  \centering
  \caption{Effect of Anti-Drug Abuse Act on the College Enrollment Rate of Adult Black Men, Comparing High and Low-Intensity States}%
  \subfloat[\centering Using adults arrests]{{\includegraphics[width=7cm]{eventstudy/high_drug_use/reducedform_ab1986.png} }}%
  \qquad
  \subfloat[\centering Using juvenile arrests]{{\includegraphics[width=7cm]{eventstudy/high_drug_use/reducedform_jb1986.png} }}%
  \label{fig:rs_es_1986}%
\end{figure}

@@

\begin{figure}[h]
  \centering
  \caption{Effect of Fair Sentencing Act on the College Enrollment Rate of Adult Black Men, Comparing High and Low-Intensity States}%
  \subfloat[\centering Using adults arrests]{{\includegraphics[width=7cm]{eventstudy/high_drug_use/reducedform_ab2010.png} }}%
  \qquad
  \subfloat[\centering Using juvenile arrests]{{\includegraphics[width=7cm]{eventstudy/high_drug_use/reducedform_jb2010.png} }}%
  \label{fig:rf_jb_es_2010}%
\end{figure}
